Inference using context-dependent models of mutation

### 2017-06-06 writeups/context-dependence.tex
relative rates

\begin{figure}
    \begin{center} 
        \includegraphics[width=\textwidth]{writeup-plots/biochem_mcmc_posteriors}
    \end{center} 
    \caption{
        Estimated average mutation rates
        for the motifs of Table \ref{tab:hominid_model}
        since the common ancestor of humans and chimpanzee.
        Rates are scaled so that the mean time to common ancestor is 0.001 units --
        if we take this to be 6 million years \citep{scally2012insights,langergraber2012generation}
        then rates are in units of mutations per 6,000 years.
        Shown are posterior medians (points) and 95\% credible intervals (lines, which are quite small in all cases).
        Figure \ref{sfig:biochem_results_zoom} shows the smaller rates in more detail.
        \label{fig:biochem_results}}
\end{figure}

@@

\begin{figure}
    \begin{center} 
        \includegraphics[width=\textwidth]{writeup-plots/biochem_mcmc_posteriors_zoomed}
    \end{center} 
    \caption{
        As in Figure \ref{sfig:biochem_results}, but with reduce vertical axis range
        to see in more detail:
        estimated average mutation rates
        for the motifs of Table \ref{tab:hominid_model}
        since the common ancestor of humans and chimpanzee.
        Rates are scaled so that the mean time to common ancestor is 0.001 units --
        if we take this to be 6 million years \citep{scally2012insights}
        then rates are in units of mutations per 6,000 years.
        Shown are posterior medians (points) and 95\% credible intervals (lines, which are quite small in all cases).
        \label{fig:biochem_results_zoom}}
\end{figure}

>>>>

\begin{figure}
    \begin{center} 
        \includegraphics[width=\textwidth]{writeup-plots/biochem_mcmc_posteriors}
    \end{center} 
    \caption{
        Estimated average mutation rates
        for the motifs of Table \ref{tab:hominid_model}
        since the common ancestor of humans and chimpanzee.
        Rates are scaled so that the mean time to common ancestor is 0.001 units --
        if we take this to be 6 million years \citep{scally2012insights,langergraber2012generation}
        then rates are in units of mutations per 6,000 years.
        Shown are posterior medians (points) and 95\% credible intervals (lines, which are quite small in all cases).
        Figure \ref{sfig:biochem_results_zoom} shows the smaller rates in more detail,
        and figure \ref{sfig:biochem_results_relative} shows the rates between categories relative to each other.
        \label{fig:biochem_results}}
\end{figure}

@@

\begin{figure}
    \begin{center} 
        \includegraphics[width=\textwidth]{writeup-plots/biochem_mcmc_posteriors_zoomed}
    \end{center} 
    \caption{
        As in Figure \ref{fig:biochem_results}, but with reduce vertical axis range
        to see in more detail:
        estimated average mutation rates
        for the motifs of Table \ref{tab:hominid_model}
        since the common ancestor of humans and chimpanzee.
        Rates are scaled so that the mean time to common ancestor is 0.001 units --
        if we take this to be 6 million years \citep{scally2012insights}
        then rates are in units of mutations per 6,000 years.
        Shown are posterior medians (points) and 95\% credible intervals (lines, which are quite small in all cases).
        \label{sfig:biochem_results_zoom}}
\end{figure}

\begin{figure}
    \begin{center} 
        \includegraphics[width=\textwidth]{writeup-plots/biochem_mcmc_posteriors_relative}
    \end{center} 
    \caption{
        As in Figures \ref{fig:biochem_results} and \ref{sfig:biochem_results_zoom}, 
        but where each rate is divided by the mean rate across all eight categories
        (as well as the 95\% credible interval endpoints).
        \label{sfig:biochem_results_relative}}
\end{figure}
